Analyzing How Organization Size, Sector, and Cybersecurity Strategies Influence Impacts on Cyberattacks

### 2024-04-10 paper/paper.qmd
testing done, llm usage updates, unwanted files removed

---
title: "TODO"
subtitle: "TODO"
author: 
  - Shivank Goel
thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
   - \usepackage{pgfplots} 
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{longtable}

>>>>

---
title: "Analyzing How Organization Size, Sector, and Cybersecurity Strategies Influence Impacts on Cyberattacks"
subtitle: "Based on Data Collected From the University of Queensland"
author: 
  - Shivank Goel
thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
date: today
date-format: long
abstract: "Undoubtedly as technology is progressing and we are stepping more closer to the digital world, the digital threats are also increasingly rapidly. This studys discusses the influence of organizational size, sector, and cybersecurity strategies on cyberattack impacts. Utilizing a dataset from the University of Queensland about data breaches and ransomware attacks from 2004 to 2019, we analyze the trends and correlations and study how different factors contribute to the severity and frequency of these incidents. Our analysis reveals key insights: larger organizations report more cyber incidents, sectors like healthcare and education are frequent targets, and cybersecurity frameworks significantly help in reducing the user impact. These findings highlight critical areas for how organizations can improve their security and protect their data.
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
   - \usepackage{pgfplots} 
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{longtable}
